Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-09-23 ms.tex
added results of GL dewar analysis on subarray 6 data.

\begin{figure*}
\gridline{\fig{raw_tser_crossDetectorS02Backsub_GLrun104.pdf}{0.48\textwidth}{Time series for S02 detector}
		\fig{raw_tser_crossDetectorS03Backsub_GLrun104.pdf}{0.48\textwidth}{Time series for S03 detector}}
		\fig{allan_var_removelinear_True_gl_across_detectors.pdf}{0.48\textwidth}{Allan variance diagram for the ratio of the S02 to S03 background-subtracted detector fluxes}
\caption{Time series for background-subtracted rectangular photometry on the S02 and S03 detectors.
The ratio of the two detectors' fluxes, after background subtraction, scales like $\sqrt{N}$ statistics down to the 200 ppm level, but how it works on longer timescales is not yet known.}\label{fig:GLtSeriesAcrossDetectors}
\end{figure*}

\subsection{Run 112}
We also investigate a slightly longer time series for GL dewar.

\begin{figure*}
\gridline{\fig{azlab_ratio_tser_gldewar_run112_sub4_hi4_no_backsub.pdf}{0.48\textwidth}{Time series for S01 / S02 Ratio No Background Sub}
\fig{azlab_ratio_tser_gldewar_run112_sub4_hi4.pdf}{0.48\textwidth}{Time series for S01 / S02 Ratio With Background Sub}}
\caption{Time series for rectangular photometry on the S01 and S02 detectors as well as background-subtracted Rectangular photometry}}\label{fig:GLtSeriesRun112}
\end{figure*}

\begin{figure*}
\gridline{\fig{all_var_gl_dewar_run112_sub4_hi4_no_backsub_removelinear_False_2.pdf}{0.48\textwidth}{Allan variance diagram no background subtraction}
\fig{all_var_gl_dewar_run112_sub4_hi4_with_backsub_removelinear_False_2.pdf}{0.48\textwidth}{Allan variance diagram with background subtraction}}
\caption{Time series for background-subtracted rectangular photometry on the S02 and S03 detectors.
The ratio of the two detectors' fluxes, after background subtraction, scales like $\sqrt{N}$ statistics down to the 200 ppm level, but how it works on longer timescales is not yet known.}\label{fig:GLtSeriesAcrossDetectors}
\end{figure*}

>>>>

\begin{figure*}
\gridline{\fig{raw_tser_crossDetectorS02Backsub_GLrun104.pdf}{0.48\textwidth}{Time series for S02 detector}
		\fig{raw_tser_crossDetectorS03Backsub_GLrun104.pdf}{0.48\textwidth}{Time series for S03 detector}}
		\fig{allan_var_removelinear_True_gl_across_detectors.pdf}{0.48\textwidth}{Allan variance diagram for the ratio of the S02 to S03 background-subtracted detector fluxes}
\caption{Time series for background-subtracted rectangular photometry on the S02 and S03 detectors.
The ratio of the two detectors' fluxes, after background subtraction, scales like $\sqrt{N}$ statistics down to the 200 ppm level, but how it works below the 100 ppm is not measurable with this test.}\label{fig:GLtSeriesAcrossDetectors}
\end{figure*}

\subsection{Run 112 - Subarray 4}
We also investigate a slightly longer time series for GL dewar.

\begin{figure*}
\gridline{\fig{azlab_ratio_tser_gldewar_run112_sub4_hi4_no_backsub.pdf}{0.48\textwidth}{Time series for S01 / S02 Ratio No Background Sub}
\fig{azlab_ratio_tser_gldewar_run112_sub4_hi4.pdf}{0.48\textwidth}{Time series for S01 / S02 Ratio With Background Sub}}
\caption{Time series for rectangular photometry on the S01 and S02 detectors as well as background-subtracted Rectangular photometry}\label{fig:GLtSeriesRun112}
\end{figure*}

\begin{figure*}
\gridline{\fig{all_var_gl_dewar_run112_sub4_hi4_no_backsub_removelinear_False_2.pdf}{0.48\textwidth}{Allan variance diagram no background subtraction}
\fig{all_var_gl_dewar_run112_sub4_hi4_with_backsub_removelinear_False_2.pdf}{0.48\textwidth}{Allan variance diagram with background subtraction}}
\caption{Allans for background-subtracted rectangular photometry on the S02 and S03 detectors.
The ratio of the two detectors' fluxes, after background subtraction, scales like $\sqrt{N}$ statistics down to the 200 ppm level, but how it works on longer timescales is not yet known.}\label{fig:GLAllanVarianceAcrossDetectors}
\end{figure*}

\subsection{Run 112 - Subarray 6}
Subarray 6 had higher lamp current and thus higher counts and lower photon noise.
It was also important to take the ratio of S01 to S03, because this pair of detectors track each other much better than the S01 /S02.

\begin{figure*}
\gridline{\fig{azlab_ratio_tser_gldewar_run112_sub6_hi4_no_backsub_biggerAp.pdf}{0.48\textwidth}{Time series for S01 / S03 Ratio No Background Sub}
\fig{azlab_ratio_tser_gldewar_run112_sub6_hi4_side_backsub_biggerAp.pdf}{0.48\textwidth}{Time series for S01 / S03 Ratio With {\it Side} Background Sub}}
\caption{Time series for rectangular photometry on the S01 and S03 detectors as well as side background-subtracted Rectangular photometry.
The background aperture was placed on the side reference pixels to reduce 1/f noise.}\label{fig:GLtSeriesRun112sub6}
\end{figure*}

\begin{figure*}
\gridline{\fig{all_var_gl_dewar_run112_sub6_hi4_side_backsub_removelinear_True_3_det_1_3.pdf}{0.48\textwidth}{Allan variance diagram with background subtraction}}
\caption{Allan variance for background-subtracted rectangular photometry on the S01 and S03 detectors.
The ratio of the two detectors' fluxes, after background subtraction, scales like $\sqrt{N}$ statistics down to the 60 ppm level where it begins to peel away from the $\sqrt{N}$ curve (green line).}\label{fig:GLAllanVarianceAcrossDetectorsSub6}
\end{figure*}
